Using the allocation scoring rule to evaluate short-term COVID-19 hospitalization forecasts during the 2021-2022 Omicron wave

### 2023-08-07 alloscore_manuscript/application.Rnw
some additional content.

ggplot(all_data,
       aes(x=mwis_rank_std, y=allo_rank_std, color=target_end_date, size=yobs)) +
  geom_point(alpha=.8) +
  scale_x_continuous("MWIS standardized rank", limits=c(0,1)) +
  scale_y_continuous("Allocation score standardized rank", limits=c(0,1)) +
  facet_wrap(.~model) +
  geom_abline(slope=1, intercept=0, linetype=2, color="gray")

@@

@@

 - different models show different levels of correlation between the metrics

@@

@@

@@

>>>>

ggplot(all_data,
       aes(x=mwis_rank_std, y=allo_rank_std, color=target_end_date, size=yobs)) +
  geom_point(alpha=.7) +
  scale_x_continuous("MWIS standardized rank", limits=c(0,1)) +
  scale_y_continuous("Allocation score standardized rank", limits=c(0,1)) +
  facet_wrap(.~model) +
  geom_abline(slope=1, intercept=0, linetype=2, color="gray")

@@

Models show differing levels of correlation between their allocation scores and MWIS values (Figure XX).
Here are some examples of the different patterns observed:
\begin{itemize}
\item positive association between allocation score and MWIS ranks: \texttt{Karlen-pypm} and \texttt{USC-SI_kJalpha} models
\item consistently strong MWIS ranks, highly variable allocation score ranks, no clear association: \texttt{JHUAPL-SLPHospEns} and \texttt{CU-select}
\item consistently strong ranks for both metrics, no clear association: \texttt{COVIDhub-ensemble}
\end{itemize}
Additionally, the \texttt{COVIDhub-baseline} model, which predicts a flat line from the most recent observation with uncertainty bounds based on a random walk, had the highest rank for allocation score in six weeks, more than any other model except the \texttt{COVIDhub-ensemble} which also had six.

<<>>=
alloscore_data_summaries |>
  group_by(model) |>
  summarize(top_rank = sum(allo_rank_std==1))
@

@@

@@

 - something here from Ben's analysis?

@@

 - It is clear that the metrics are capturing different aspects of performance

@@

 - the fact that it is hard to beat the baseline for allocation suggests that we are not consistently adding value over just looking at the current levels. \ngr{although is there something more to it about how the baseline accounts for uncertainty?}
